---
CSCI 4502 Project
Climate Change since 1750
Xinyi Zhang
March 29, 2017
This code plot temperature of the China in 1950, and 2013.
---
Loading the necessarily package and input dataset:
```{r, message=FALSE,warning=FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)
library(choroplethr)
library(choroplethrMaps)
library(choroplethrAdmin1)

df <- fread("../input/GlobalLandTemperaturesByState.csv",showProgress =  FALSE)

```

Formatting the dataset and selecting the columns we are gonna use:
```{r}
df_China<-na.omit(df)
df_China <- df_China %>%
  filter(Country=="China") %>%
  separate(col = dt, into = c("Year", "Month", "Day"), convert = TRUE) 
df_China2 <- df_China %>% 
              select(Year,AverageTemperature,State) %>%
              group_by(Year,State) %>%
              dplyr:: summarise(value=mean(AverageTemperature))
```

Average temperatures in China for the year 1950:
Modified the names of Chinese province as these names in the admin1choropleth package are differnet than the names in our dataset.
```{r}
colnames(df_China2)[2]<- "region"
df_China2$region<-tolower(df_China2$region)
df_China1950 <- df_China2 %>%
             filter(Year==1950) 
df_China1950 <- df_China1950[,2:3]

df_China1950$region <- paste(df_China1950$region , "sheng", sep=" ")
df_China1950$region[2] <- paste("beijing shi")
df_China1950$region[3] <- paste("chongqing shi")
df_China1950$region[7] <- paste("guangxi zhuangzu zizhiqu")
df_China1950$region[19] <- paste("inner mongolia autonomous region")
df_China1950$region[20] <- paste("ningxia huizu zizhiqu")
df_China1950$region[22] <- paste("shaanxi")
df_China1950$region[24] <- paste("shanghai shi")
df_China1950$region[27] <- paste("tianjin shi")
df_China1950$region[28] <- paste("xinjiang uygur zizhiqu")
df_China1950$region[29] <- paste("tibet autonomous region")

admin1_choropleth(country.name = "china", df_China1950, title = "Average Temperatures in China (1950)")
```

Average temperatures in China for the year 2013:
```{r}
df_China2013 <- df_China2 %>%
             filter(Year==2013) 
df_China2013 <- df_China2013[,2:3]

df_China2013$region <- paste( df_China2013$region , "sheng", sep=" ")
df_China2013$region[2] <- paste("beijing shi")
df_China2013$region[3] <- paste("chongqing shi")
df_China2013$region[7] <- paste("guangxi zhuangzu zizhiqu")
df_China2013$region[19] <- paste("inner mongolia autonomous region")
df_China2013$region[20] <- paste("ningxia huizu zizhiqu")
df_China2013$region[22] <- paste("shaanxi")
df_China2013$region[24] <- paste("shanghai shi")
df_China2013$region[27] <- paste("tianjin shi")
df_China2013$region[28] <- paste("xinjiang uygur zizhiqu")
df_China2013$region[29] <- paste("tibet autonomous region")

admin1_choropleth(country.name = "china", df_China2013,title = "Average Temperatures in China (2013)")
```

Average temperature increase in China between 1950 and 2013:
```{r, message=FALSE,warning=FALSE}
diff_1950_2013 <- as.data.frame(df_China2013$value-df_China1950$value)
diff_1950_2013<- cbind(df_China2013$region, diff_1950_2013)
colnames(diff_1950_2013)[1]<- "region"
colnames(diff_1950_2013)[2]<- "value"
admin1_choropleth(country.name = "china", diff_1950_2013,title = "Average Temperature Increase in China (1950-2013)")
```

Average temperature in the upper part of China from 1950 to 2013
Pick "Nei Mongu", "Gansu", and "Qinghai" as examples for the upper parts of China. 
```{r, message=FALSE,warning=FALSE}

df_China_Inner <- df_China %>% 
              filter(State=="Nei Mongol" | State =="Gansu" | State =="Qinghai" ) %>%
              filter(Year>1950) %>%
              group_by(Year,State)%>%
              dplyr:: summarise(AverageTemperature=mean(AverageTemperature))

ggplot(df_China_Inner, aes(x=Year, y=AverageTemperature)) +
               geom_point(color='red') +
               facet_wrap(~ State)+
               geom_smooth()
```

Average temperature in the middle part of China from 1950 to 2013
Pick "Chongqing", "Hubei", and "Yunnan" as examples for the upper parts of China.
```{r, message=FALSE,warning=FALSE}

df_China_Middle <- df_China %>% 
              filter(State=="Chongqing" | State =="Hubei" | State =="Yunnan" ) %>%
              filter(Year>1950) %>%
              group_by(Year,State)%>%
              dplyr:: summarise(AverageTemperature=mean(AverageTemperature))

ggplot(df_China_Middle, aes(x=Year, y=AverageTemperature)) +
               geom_point(color='red') +
               facet_wrap(~ State)+
               geom_smooth()
```

Average temperature in the coastal part of China from 1950 to 2013
Pick "Guangdong", "Fujian", and "Guangxi" as examples for the upper parts of China. 
```{r, message=FALSE,warning=FALSE}

df_China_Coastal <- df_China %>% 
              filter(State=="Guangdong" | State =="Fujian" | State =="Guangxi" ) %>%
              filter(Year>1950) %>%
              group_by(Year,State)%>%
              dplyr:: summarise(AverageTemperature=mean(AverageTemperature))

ggplot(df_China_Coastal, aes(x=Year, y=AverageTemperature)) +
               geom_point(color='red') +
               facet_wrap(~ State)+
               geom_smooth()

```