---
CSCI 4502 Project
Climate Change since 1750
Xinyi Zhang
March 29, 2017
This code plot temperature of the United States in 1850, 1980, and 2013.
---
Loading the necessarily package and input dataset:
```{r, message=FALSE,warning=FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)
library(choroplethr)
library(choroplethrMaps)
library(choroplethrAdmin1)

df <- fread("GlobalLandTemperaturesByState.csv",showProgress =  FALSE)

```

Formatting the dataset and selecting the columns we are gonna use:
Change the name of "Georgia (State)" into "Georgia" as the package has different name of Georgia state than the dataset has
```{r}
df_United_States<-na.omit(df)
df_United_States <- df_United_States %>%
  filter(Country=="United States") %>%
  separate(col = dt, into = c("Year", "Month", "Day"), convert = TRUE) 

df_United_States$State <- as.character(df_United_States$State)
df_United_States$State[df_United_States$State=="Georgia (State)"] <- "Georgia"
df_United_States$State<- as.factor(df_United_States$State) 


df_United_States2 <- df_United_States %>% 
              select(Year,AverageTemperature,State) %>%
              group_by(Year,State) %>%
              dplyr:: summarise(value=mean(AverageTemperature))
```

1850 representing the developing time after the immigration period
Average temperatures in the United States in 1850:
```{r}
colnames(df_United_States2)[2]<- "region"
df_United_States2$region<-tolower(df_United_States2$region)
df_United_States1850 <- df_United_States2 %>%
             filter(Year==1850) 
df_United_States1850 <- df_United_States1850[,2:3]

state_choropleth(df_United_States1850,
                 title= "Average Temperatures of United States in 1850", 
                 legend="Temperature Range")
```

Average temperatures in the United States in 1980:
```{r}
colnames(df_United_States2)[2]<- "region"
df_United_States2$region<-tolower(df_United_States2$region)
df_United_States1980 <- df_United_States2 %>%
             filter(Year==1980) 
df_United_States1980 <- df_United_States1980[,2:3]

state_choropleth(df_United_States1980,
                 title= "Average Temperatures of United States in 1980", 
                 legend="Temperature Range")
```

Average temperatures in the United States in 2013:
```{r}
colnames(df_United_States2)[2]<- "region"
df_United_States2$region<-tolower(df_United_States2$region)
df_United_States2013 <- df_United_States2 %>%
             filter(Year==2013) 
df_United_States2013 <- df_United_States2013[,2:3]

state_choropleth(df_United_States2013,
                 title= "Average Temperatures of United States in 2013", 
                 legend="Temperature Range")
```

Compare the average temperature between 1850 and 2013:
```{r, message=FALSE,warning=FALSE}
diff_1850_2013 <- as.data.frame(df_United_States2013$value-df_United_States1850$value)
diff_1850_2013<- cbind(df_United_States2013$region, diff_1850_2013)
colnames(diff_1850_2013)[1]<- "region"
colnames(diff_1850_2013)[2]<- "value"
state_choropleth(diff_1850_2013,
                 title= "Average Temperature Change of United States from 1949 to 2013", 
                 legend="Changes")
```
